Supplementary Information

### 2015-09-08 manuscript/supplement.tex
Bibliographies are done

    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection \\
        \hline
        Alamitos & 1 & \cite{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
        Alford & 1 & \cite{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
        Beaver & 1 & \cite{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
        Bere  & 1 & \cite{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
        Bridge & 1 & \cite{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
        Broad & 1 & \cite{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
        Broadstone & 1 & \cite{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
        Calero & 1 & \cite{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
        Canton & 1 & \cite{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
        Carpinteria2006 & 1 & \cite{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
        Chub  & 1 & \cite{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
        Coachella & 1 & \cite{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
        Connery & 1 & \cite{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
        Corte & 1 & \cite{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
        Coyote & 1 & \cite{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
        German & 1 & \cite{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
        GrandeCl & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        GrandeSc & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        Guadalupe & 1 & \cite{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
        Hainich   & 1 & Unpublished  & terrestrial &       & No    & Could not locate original source \\
        LittleKyeBurn & 1 & \cite{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
        LittleRock & 1 & \cite{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
        Mondego & 1 & \cite{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        Montane Forest & 1 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
        Reef  & 1 & \cite{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
        Sierra & 1 & \cite{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
        SimberloffE1 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
        SimberloffE2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
        SimberloffE3 & 1 & \cite{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
        SimberloffE7 & 1 & \cite{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
        SimberloffE9 & 1 & \cite{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
        SimberloffST2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
        Skipwith & 1 & \cite{Warren1989}  & lake  & 53,40 N & Yes   &       \\
        Stink & 1 & \cite{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
        StMarks & 1 & \cite{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
        Stony  & 1 & \cite{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
        TreleaseWoods & 1 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
        Tuesday & 1 & \cite{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
        Weddell Sea & 1 & \cite{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
        Ythan & 1 & \cite{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
        BahiaDunne & 2 & \cite{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
        CarpinteriaDunne & 2 & \cite{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
        EsteroDunne & 2 & \cite{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
        FjordDunne & 2 & \cite{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
        OtagoDunne & 2 & \cite{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
        SyltDunne & 2 & \cite{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
        YthanDunne & 2 & \cite{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
        1     & 3 & \cite{Qazim1970}  & estuary &       & No    & Could not locate original source \\
        2     & 3 & \cite{Day1967} & estuary &       & No    & Could not locate original source \\
        3     & 3 & \cite{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
        5     & 3 & \cite{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
        6     & 3 & \cite{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
        7     & 3 & \cite{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
        8     & 3 & \cite{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
        9     & 3 & \cite{Kitching1967}  & stream &       & No    & Could not locate original source \\
        10    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        11    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        12    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        13    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        14    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalised scheme \\
        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
        19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
        20    & 3 & \cite{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
        21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
        28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalised scheme \\
        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalised scheme \\
        31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
      \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Smirnov1961}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        270   & 3 & \cite{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
        271   & 3 & \cite{Amundsen2013}  & lake  & 69,07 N & Yes   &        \\
        272   & 3 & \cite{Hampton2011}    & lake  & 48,03,29 N & Yes   &       \\
        273   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
        274   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
        275   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
        276   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
        277   & 3 & \cite{Massana1996}  & lake  & 42,08,6 - 42,07 N & Yes   &       \\
        278   & 3 & \cite{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
        279   & 3 & \cite{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
        280   & 3 & \cite{Cromar1996}  & stream & 43,58 N & Yes   &       \\
        281   & 3 & \cite{Cromar1996}  & stream & 44,58 N & Yes   &       \\
        282   & 3 & \cite{Cromar1996}  & stream & 45,58 N & Yes   &       \\
        283   & 3 & \cite{Cromar1996}  & stream & 46,58 N & Yes   &       \\
        284   & 3 & \cite{Cromar1996}  & stream & 47,58 N & Yes   &       \\
        285   & 3 & \cite{Cromar1996}  & stream & 48,58 N & Yes   &       \\
        286   & 3 & \cite{Cromar1996}  & stream & 49,58 N & Yes   &       \\
        287   & 3 & \cite{Cromar1996}  & stream & 50,58 N & Yes   &       \\
        288   & 3 & \cite{Christian1999}    & estuary & 30,05,39 N & Yes   &       \\
        289   & 3 & \cite{Fetahi2011}  & lake  & 11,15 N & Yes   &       \\
        290   & 3 & \cite{Brodeur1992}    & marine & 43 - 48 N & Yes   &       \\
        291   & 3 & \cite{Brodeur1992}    & marine & 44 - 48 N & Yes   &       \\
        292   & 3 & \cite{Brodeur1992}    & marine & 45 - 48 N & Yes   &       \\
        293   & 3 & \cite{Brodeur1992}    & marine & 46 - 48 N & Yes   &       \\
        294   & 3 & \cite{Gaedke1994}  & lake  & 47,37,30 N & Yes   &       \\
        295   & 3 & \cite{Preston2012}    & lake  & 37.66 N & Yes   &        \\
        296   & 3 & \cite{Ratsirarson1996}  & lake  & 24,55 S & Yes   &       \\
        297   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        298   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        299   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        300   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        301   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        302   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
        303   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
         \hline
      \end{tabular}}%
      \end{table}

>>>>

    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection \\
        \hline
        Alamitos & 1 & \cite{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
        Alford & 1 & \cite{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
        Beaver & 1 & \cite{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
        Bere  & 1 & \cite{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
        Bridge & 1 & \cite{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
        Broad & 1 & \cite{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
        Broadstone & 1 & \cite{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
        Calero & 1 & \cite{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
        Canton & 1 & \cite{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
        Carpinteria2006 & 1 & \cite{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
        Chub  & 1 & \cite{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
        Coachella & 1 & \cite{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
        Connery & 1 & \cite{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
        Corte & 1 & \cite{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
        Coyote & 1 & \cite{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
        German & 1 & \cite{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
        GrandeCl & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        GrandeSc & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
        Guadalupe & 1 & \cite{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
        Hainich   & 1 & Unpublished  & terrestrial &       & No    & Could not locate original source \\
        LittleKyeBurn & 1 & \cite{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
        LittleRock & 1 & \cite{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
        Mondego & 1 & \cite{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
        Montane Forest & 1 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
        Reef  & 1 & \cite{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
        Sierra & 1 & \cite{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
        SimberloffE1 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
        SimberloffE2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        SimberloffE3 & 1 & \cite{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
        SimberloffE7 & 1 & \cite{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
        SimberloffE9 & 1 & \cite{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
        SimberloffST2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
        Skipwith & 1 & \cite{Warren1989}  & lake  & 53,40 N & Yes   &       \\
        Stink & 1 & \cite{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
        StMarks & 1 & \cite{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
        Stony  & 1 & \cite{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
        TreleaseWoods & 1 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
        Tuesday & 1 & \cite{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
        Weddell Sea & 1 & \cite{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
        Ythan & 1 & \cite{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
        BahiaDunne & 2 & \cite{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
        CarpinteriaDunne & 2 & \cite{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
        EsteroDunne & 2 & \cite{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
        FjordDunne & 2 & \cite{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
        OtagoDunne & 2 & \cite{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
        SyltDunne & 2 & \cite{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
        YthanDunne & 2 & \cite{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
        1     & 3 & \cite{Qazim1970}  & estuary &       & No    & Could not locate original source \\
        2     & 3 & \cite{Day1967} & estuary &       & No    & Could not locate original source \\
        3     & 3 & \cite{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
        4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
        5     & 3 & \cite{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
        6     & 3 & \cite{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
        7     & 3 & \cite{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
        8     & 3 & \cite{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
        9     & 3 & \cite{Kitching1967}  & stream &       & No    & Could not locate original source \\
        10    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        11    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
        12    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        13    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
        14    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalised scheme \\
        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
        19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
        20    & 3 & \cite{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
        21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
        27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
        28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalised scheme \\
        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalised scheme \\
        31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
      \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
        58    & 3 & \cite{Smirnov1961}  & lake & 51,46 N & Yes   &       \\
        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
        63    & 3 & \cite{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
        64    & 3 & \cite{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
        65    & 3 & \cite{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
        66    & 3 & \cite{Mann1972a}  & stream & 51,30 N & Yes   &       \\
        67    & 3 & \cite{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
        68    & 3 & \cite{Morgan1972}  & lake &       & No    & Could not locate original source \\
        69    & 3 & \cite{Cohen1990}  & estuary &       & No    & Could not locate original source \\
        70    & 3 & \cite{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
        71    & 3 & \cite{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
        72    & 3 & \cite{Baril1983}  & lake & 46,02 N & Yes   &       \\
        73    & 3 & \cite{Schiemer1979}  & lake &       & No    & Could not locate original source \\
        74    & 3 & \cite{Brown1964} & marine & 34,15,00 S & Yes   &       \\
        75    & 3 & \cite{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
        76    & 3 & \cite{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
        77    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        78    & 3 & \cite{Burgis1972}  & lake & 0     & Yes   &       \\
        79    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        80    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
        81    & 3 & \cite{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
        82    & 3 & \cite{Cohen1990} & marine &       & No    & Could not locate original source \\
        83    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
        84    & 3 & \cite{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
        85    & 3 & \cite{Mizuno1982}  & lake &       & No    & Could not locate original source \\
        \hline
      \end{tabular}}%
      \end{table}

@@

    \begin{table}[h!]
    \centering
    {\footnotesize
      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
        \hline
        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
        \hline
        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalised scheme \\
        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
        \hline
      \end{tabular}%
        }
    \end{table}%
